Bayes network classifiers for fMRI

### 2012-10-16 article/article.tex
Added some notes to article, added relative loading of data
Added __main__ to framework to prevent auto-run after import
Article and bibtex update

\documentclass[preprint,journal]{vgtc}
\let\ifpdf\relax
%% Uncomment one of the lines above depending on where your paper is
%% in the conference process. ``review'' and ``widereview'' are for review
%% submission, ``preprint'' is for pre-publication, and the final version
%% doesn't use a specific qualifier. Further, ``electronic'' includes
%% hyperreferences for more convenient online viewing.

@@

%% indicate IEEE Member or Student Member in form indicated below
\author{Mattijs Meiboom, Robin Mills, Tijn Schouten, Spyros Ioakeimidis}
\authorfooter{
\item
  Mattijs Meiboom is with University of Groningen, E-mail: .
\item
  Robin Mills is with University of Groningen, E-mail: .
\item
  Tijn Schouten is University of Groningen, E-mail: .
\item
  Spyros Ioakeimidis  is with University of Groningen, E-mail: spyrosikmd@gmail.com.
}

@@

%% Abstract section.
\abstract{
 This is the abstract section...
} % end of abstract

%% Keywords that describe your work. Will show as 'Index Terms' in journal
%% please capitalize first letter and insert punctuation after last keyword
\keywords{}

@@

%% The ``\maketitle'' command must be the first command after the
%% ``\begin{document}'' command. It prepares and prints the title block.

%% the only exception to this rule is the \firstsection command
\firstsection{Introduction}

\maketitle

>>>>

%% This paper describes the results of the Machine Learning practical
%% project. It should be approximately 8 pages long and contain the
%% following sections:
%%
%% 1) Title, authors, abstract
%% 2) Introduction
%% 3) Application
%% 4) Methods
%% 5) Experimental Results
%% 6) Discussion / Conclusion
%% References
\documentclass[preprint,journal]{vgtc}
\let\ifpdf\relax
%% Uncomment one of the lines above depending on where your paper is
%% in the conference process. ``review'' and ``widereview'' are for review
%% submission, ``preprint'' is for pre-publication, and the final version
%% doesn't use a specific qualifier. Further, ``electronic'' includes
%% hyperreferences for more convenient online viewing.

@@

%% indicate IEEE Member or Student Member in form indicated below
\author{Mattijs Meiboom, Robin Mills, Tijn Schouten, Spyros Ioakeimidis}
\authorfooter{
\item
  Mattijs Meiboom is with University of Groningen, E-mail: m.meiboom@student.rug.nl.
\item
  Robin Mills is with University of Groningen, E-mail: .
\item
  Tijn Schouten is University of Groningen, E-mail: t.m.schouten.2@student.rug.nl.
\item
  Spyros Ioakeimidis  is with University of Groningen, E-mail: spyrosikmd@gmail.com.
}

@@

%% Abstract section.
\abstract{
Functional magnetic resonance imaging (fMRI) is a brain mapping technique that allows researchers to measure activity in a subject's brain. This technique is typically used to determine which areas of the brain are involved in performing a certain task. Using this knowledge, we may also be able to determine what task was performed by looking at fMRI data. In this paper, we will discuss the use of machine learning algorithms for the classification of fMRI data. By using classifiers we will try to predict what stimulus a subject is looking at, based on the brain activity during that time.
} % end of abstract

%% Keywords that describe your work. Will show as 'Index Terms' in journal
%% please capitalize first letter and insert punctuation after last keyword
\keywords{fMRI, Machine learning, Classification.}

@@

%% The ``\maketitle'' command must be the first command after the
%% ``\begin{document}'' command. It prepares and prints the title block.
%% the only exception to this rule is the \firstsection command
\firstsection{Introduction}
\maketitle
%% Now the actual contents of first section
- basic terms introduced (fmri, classification, ...)
- related work and results
- state of the art: multivariate pattern analysis (\cite{Haxby2012852})
- structure of rest of the paper
\section{Application}
- prediction
- cognitive state
\section{Methods}
- supervised learning
- naive bayes
- multivariate
- pca
- comparison
- classifying subtrials vs trials (ie 54 vs 27)

\subsection{Data acquisition and dimensions}
The dataset used for our experiments was originally collected by Marcel Just et al. from Carnegie Mellon University's Center for Cognitive Brain Imaging and published as the StarPlus fMRI dataset. This set consists of fMRI data for 6 subjects that was obtained while having each subject participate in a number of trials.

In these trials, subjects were presented with a stimulus on a computer screen. This stimulus was either a picture or a sentence. After a period of time, the stimulus would be replaced with a stimulus of the opposite type (i.e. picture with sentence and vice versa) after which the subject would indicate by pressing a button whether the sentence correctly described the picture. At the end of each trial, approximately 54 fMRI scans have be taken with an interval of 500ms.
The entire dataset consist of voxel data and metadata providing information about the dataset. Included in this information is not only the trial and scan each voxel belongs to, but also the type of the trial (picture first or sentence first). This makes the dataset suitable for classification using supervised learning.

In total, we have data available for approximately 4000 voxels per scan, 54 scans per trial, 40 trials per subject, 6 subjects.

\section{Experimental Results}
\section{Discussion / Conclusion}
